\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{4.1pt}


% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeEducationSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textbf{\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
    \textbf{\Huge \scshape\textbf{\Large Bat-Orgil Erdenebat }} \\ \vspace{1pt}
    \small (662) 380-7252 $|$ \href{mailto:batorgilrb@gmail.com}{\underline{batorgilrb@gmail.com}} $|$ 
    \href{https://github.com/BatOrgil7}{\underline{github.com/BatOrgil7}} $|$ {\underline{\href{https://linkedin.com/in/bat-orgil-erdenebat}{linkedin.com/in/bat-orgil-erdenebat}}} $|$ {{Memphis, TN}}
\end{center}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEducationSubheading
      {University of Mississippi}{Oxford, MS}
      {Bachelor of Science in Computer Science – Data Science Emphasis; Math Minor, \textbf{GPA: 3.78}}{\textnormal{Expected May 2027}} 
    \resumeSubHeadingListEnd
    \begin{itemize}[leftmargin=0.20in, label={}]
    \small{\item{
    \textbf{Relevant Coursework:} Algorithms \& Data Structure Analysis, Combinatorics, Linear Algebra, Statistics, Machine Learning, Database Systems, Information Visualization, Operating Systems, Computer Organization \\
    \textbf{Awards:} Freeman Grant - \$9,000, Chancellor's Honor Roll Fall 2024, Spring 2025 \\
    \textbf{Certifications:} Machine Learning Foundations e-Certificate (Cornell University) Break Through Tech August 2026; Career Essentials in Generative AI (Microsoft, LinkedIn) June 2024
    }}
  \end{itemize}
  
%-----------TECHNICAL SKILLS-----------------

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.20in, label={}]
    \small{\item{
     \textbf{Languages:} Python, R, Java, SQL, C++, Rust, JavaScript, TypeScript, C, LaTeX, Assembly\\
     \textbf{Libraries/Frameworks:} PyTorch/Keras, TensorFlow, Hugging Face Transformers, Scikit-learn, OpenCV, Pandas, NumPy, MediaPipe, Flask, Tailwind CSS, Matplotlib, Seaborn \\
     \textbf{Tools/Platforms:} Linux, Git, GitHub, Neo4j, Google Cloud, MongoDB, MySQL, Docker, Figma, GitLab, AWS
    }}
  \end{itemize}

%-----------EXPERIENCE-----------------

\section{Professional Experience}
    \resumeSubHeadingListStart

        \resumeSubheading
        {Break Through Tech}{New York, NY}
        {AI Studio Fellow}{May 2026 – Present}
        \resumeItemListStart
            \resumeItem{Selected from \textbf{4,000+} applicants nationwide for a one-year AI fellowship focused on machine learning, data science, mentorship, and career readiness.}
            \resumeItem{Preparing for AI Studio challenge projects with industry advisors to deliver real-world ML solutions and portfolio-ready work.}
        \resumeItemListEnd
        
        \resumeSubheading
        {PotatoNet Co., Ltd.}{Seoul, South Korea}
        {Machine Learning Engineering Intern}{June 2026 - Present}
        \resumeItemListStart
            \resumeItem{Extracted a CNN-LSTM-Attention fault predictor (\textbf{94.7\%} accuracy) from a legacy Django monolith into a clean FastAPI service on a 16-container microservices platform, and migrated an internal LSTM service to an Nginx → Gunicorn → Django + TLS stack with zero-downtime, reusable deployments.}
            \resumeItem{Built and shipped a production graph-ETL pipeline that backfilled 6 months of threat data into a live Neo4j store (\textbf{19.4K} malicious-JS nodes, 13.7K domains, 3.9K IPs) via idempotent, rollback-tagged loads automated as a nightly self-healing cron job, and deduplicated 267K scripts with SimHash LSH into a leak-free 12.4K-example training set.}
            \resumeItem{Engineered a 7-signal attacker-profiling engine that clusters malicious JavaScript into named ``families'' (SimHash AST similarity, perceptual screenshot hashing, and shared TLS-cert/IP/ASN/registrant infrastructure) via GDS Leiden community detection, then diagnosed and fixed a 52K-script over-merge caused by benign library bridges — cutting max family size to \textbf{476} across 334 clean families.}
          \resumeItemListEnd
          
        \resumeSubheading
        {University of Mississippi – Dept. of Computer \& Information Science}{Oxford, MS}
        {Teaching Assistant \& Computer Science Tutor}{August 2025 – Present}
        \resumeItemListStart
            \resumeItem{Led hands-on labs for \textbf{200+} STEM students across four courses (Data Structures and Algorithms), lifting Python, Java, and OOP proficiency by coaching students through debugging, optimization, and algorithmic reasoning.}
            \resumeItem{Raised academic performance for \textbf{50+} mentees by delivering individualized tutoring in Python, Java, and Data Structures \& Algorithms, reinforcing programming fundamentals and independent problem-solving.}
        \resumeItemListEnd
    
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Census Income Classification}\;|\;\href{https://github.com/BatOrgil7/census-income-ml-pipeline}{\underline{github.com/BatOrgil7/census-income-ml-pipeline}}}{}
    \resumeItemListStart
      \resumeItem{Built an end-to-end ML pipeline on the U.S. Census Income dataset (32K+ records) to predict annual income. EDA, median imputation, log-transform of skewed features, one-hot encoding, and leakage-free scaling used. Tuned logistic regression via GridSearchCV, scoring on F1 to address class imbalance rather than misleading accuracy.}
      \resumeItem{Implemented a 3-layer Keras neural network for the same task and found it only matched logistic regression on F1 (0.70 vs 0.68), concluding the simpler, interpretable model was preferable for this tabular problem.}
      \resumeItem{Audited model coefficients for fairness and surfaced a discrimination risk, informing a recommendation against naive deployment for lending use.}
    \resumeItemListEnd
    
  \resumeProjectHeading
    {\textbf{Streaming Evaluation Protocol for CSLR}\;|\;\href{https://github.com/BatOrgil7/signstream-eval}{\underline{github.com/BatOrgil7/signstream-eval}}}{}
    \resumeItemListStart
      \resumeItem{Designed a standardized evaluation protocol for streaming sign language recognition, adapting latency/stability metrics from streaming ASR and simultaneous MT to fill a gap left by offline-only benchmarks.}
      \resumeItem{Constructed a fault-tolerant landmark extraction pipeline (multiprocessing, content-addressed caching, failure-manifest tracking) processing PHOENIX-2014T across video and frame-folder formats.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
