\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{4.1pt}


% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular•}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
    \textbf{\Huge \scshape\textbf{\Large Bat-Orgil Erdenebat }} \\ \vspace{1pt}
    \small +1-662-380-7252 $|$ \href{mailto:batorgilrb@gmail.com}{\underline{batorgilrb@gmail.com}} $|$ 
    \href{https://github.com/BatOrgil7}{\underline{https://github.com/BatOrgil7}} $|$ {\underline{\href{https://linkedin.com/in/bat-orgil-erdenebat}{https://linkedin.com/in/bat-orgil-erdenebat}}}
\end{center}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Mississippi}{Oxford, MS}
      {B.S. in Computer Science – Data Science Emphasis; Math Minor; \textbf{GPA: 3.78}}{August 2023 - May 2027}
      \\[0.25em]
      {\textbf{Honors:} Sally McDonnell Barksdale Honors College (SMBHC)}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------

\section{Professional Experience}
    \resumeSubHeadingListStart

        \resumeSubheading
        {Break Through Tech AI Program, Cornell Tech}{Remote}
        {AI/ML Fellow}{May 2026 – Present}
        \resumeItemListStart
            \resumeItem{Selected from \textbf{4,000+} applicants nationwide for a one-year AI fellowship focused on machine learning, data science, mentorship, and career readiness.}
            \resumeItem{Completing a 9-week ML Foundations curriculum using industry-relevant tools to analyze data, build pipelines, and train and validate ML models.}
            \resumeItem{Preparing for AI Studio challenge projects with industry advisors to deliver real-world ML solutions and portfolio-ready work.}
        \resumeItemListEnd

        \resumeSubheading
        {University of Mississippi – Dept. of Computer \& Information Science}{Oxford, MS}
        {Teaching Assistant – CIS 356, CIS 112, \& CIS 111}{August 2025 – Present}
        \resumeItemListStart
            \resumeItem{Led labs for \textbf{100+} CS and STEM students across Data Structures in Python, Computer Science I, and Computer Science II, strengthening Python, Java, OOP, algorithms, and core data structures.}
            \resumeItem{Coached students through debugging, optimization, and algorithmic reasoning, improving code clarity and problem-solving readiness.}
        \resumeItemListEnd
        \resumeSubheading
        {University of Mississippi – Dept. of Computer \& Information Science}{Oxford, MS}
        {Computer Science Tutor}           {January 2026 – Present}
        \resumeItemListStart
        \resumeItem{Provided one-on-one tutoring in programming, data structures, debugging, and introductory AI/ML concepts for coursework and exam preparation.}
        \resumeItemListEnd
        \resumeSubheading
          {American Cultural \& Information Center}{Ulaanbaatar, Mongolia}
          {Intern}{Sep 2022 - May 2023}
          \resumeItemListStart
            \resumeItem
            {Built website front-end assets and branded digital content with HTML, CSS, Figma, Canva, and Photoshop, improving user experience and marketing consistency.}
            \resumeItem
            {Supported targeted campaigns reaching \textbf{356,000+} people and produced brand/system design guidelines for consistent communications.}
          \resumeItemListEnd
    
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Research and Project}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Real-Time ASL-to-Text Recognition System} $|$ OpenCV, MediaPipe, TensorFlow, Matplotlib, scikit-learn}{}
    \resumeItemListStart
      \resumeItem{Developed a Computer Vision pipeline using OpenCV and MediaPipe for robust Hand Tracking and Landmark Detection, enabling structured feature extraction from live webcam input.}
      \resumeItem{Designed and trained a Deep Learning CNN model in TensorFlow/Keras for ASL alphabet classification, achieving 97.19\% accuracy on validation data.}
      \resumeItem{Optimized the system for low-latency Real-Time Inference, integrating preprocessing, model prediction, and text output into a responsive end-to-end deployment pipeline.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{CS2 Esports Analytics Platform} $|$ SQL, Database Design, Data Modeling}{}
    \resumeItemListStart
      \resumeItem{Engineered normalized relational database and developed complex SQL queries using aggregate functions, nested subqueries, and percentile ranking to identify players; detect outliers in performance distribution}
      \resumeItem{Designed data model enabling correlation analysis between map-specific performance, team composition factors, and win probability, with schema optimized for regression-ready data extraction and cohort analysis across tournament tiers}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Certifications and Awards-----------------
\section{Certifications and Awards}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Freeman Grant}{}
      {Croft Institute for International Studies, University of Mississippi; South Korea Internship}{Awarded 2026}

    \resumeSubheading
      {Career Essentials in Generative AI by Microsoft}{}
      {Microsoft}{Issued June 2024}
      
    \resumeSubheading
      {Ethics in the Age of Generative AI}{}
      {LinkedIn} {Issued June 2024}
  \resumeSubHeadingListEnd

\end{document}
